---
title: "Report -- Reconstruct Individual Patient Data from Published Survival Curves Using IPDfromKM Package"
author: Na Liu, J. Jack Lee
date: '`r format(Sys.time(), "%d %B, %Y")`'
---
```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}
list.of.packages <- c("ggplot2", "survival","boot","DT","shiny","shinyjs",
                      "cowplot","ggpubr","gridExtra","knitr","devtools")
lapply(list.of.packages,library,character.only = TRUE)
devtools::install_github("NaLiuStat/IPDfromKM")
library(IPDfromKM)
```


```{r include=FALSE}
knitr::opts_chunk$set(fig.width=8, fig.height=5, 
               echo=FALSE, 
               warning=FALSE, message=FALSE, 
               cache=TRUE)
```


The individual patient data (IPD) approach has been considered as the gold standard to improve the reliability of clinical data analysis. This shiny application use R package IPDfromKM to reconstruct the life-table of individual patients from published Kaplan-Meier survival curves. The coordinates of curves can be extracted from digitize software programs like [DigitizeIt](<https://www.digitizeit.de>) or [ScanIt](<https://www.amsterchem.com/scanit.html>). In the help file we showed the optimal procedures to get the high quality data from the survival curves. So we assume the read-in dataset is the good representation of the original published curve.  


```{r  include=FALSE,results='hide',tidy=TRUE}
pre <- eventReactive(input$go,{
         preprocess(dat=mydata(),trisk=trisk(),nrisk=nrisk(),
                    totalpts=totalpts(),maxy=maxy())
         })
mylist <- eventReactive(input$go,{
    getIPD(prep=pre(),armind=armind(),tot.events=totalevent())
  })

```

## Evaluate the Accuracy of Reconstruction
The reconstruct IPD in CSV file can be download by click the "DownloadIPD" button in the shiny page. Below shows the head of reconstructed IPD data:


```{r }
kable(head(mylist()[[1]]), digits = 2)
```

We can calculate a new survival curve from the reconstructed IPD using the R survfit function. Then compare the new curves with the read-in dataset.

```{r }
plotIPD(est=mylist(),ori_dat=mydata(),maxy=maxy())
```

The summary of estimation accuracy:
```{r }
kable(head(mylist()[[8]]), digits = 3)
```

## Graph Survival Curves
```{r tidy=TRUE}
survreport(ipd1=mylist()[[1]],arms=1,interval=6)
```

